{\itshape Advanced Robotics} A simple path optimization method for motion planning

### 2016-01-07 paper.tex
Change Geraerts reference from ICRA to IJRR

For this shortening purpose, random shortcut (RS) methods are
still very 
popular~\cite{Sekhavat-Svestka1998,Geraerts04clearancebased,HauserFastSmooth}. 
However, RS requires fine 
tuning of the termination condition and is no efficient for long 
trajectories where only a minor part needs to be optimized, 
as in Figure~\ref{local_box_optim}.
Figure~\ref{decoupled_DOF_optimization} presents another situation where RS 
will always fail to optimize the initial path, since it cannot decouple the 
robot degrees of freedom (DOF) on which the optimization occurs. This problem is 
addressed by our method.

@@

Some heuristics use random shortcuts on the initial guess combined with a 
trajectory re-building. For example,~\cite{HauserFastSmooth} returns smooth shortcuts made of parabola and line combinations, relying on the classical bang-bang control approach. These local refined trajectories 
are time-optimal since they comply with acceleration and velocity constraints. 
Also based on random shooting,~\cite{Guernane2011} is guiding 
configuration-generation with local holonomic considerations. 
Nevertheless this method remains only 
locally optimal, and is not addressing high-DOF 
problems.~\cite{Geraerts04clearancebased} is 
using medial axis retraction for clearance and a PRS (shortcut is applied only 
on some random DOF) 
which can address the problem of Figure~\ref{decoupled_DOF_optimization}. 
However it is 
relatively slower than RS, and~\cite{Geraerts04clearancebased} only investigates 
it for freeflyer robots. 
Furthermore PRS is not taking advantage of information returned by 
the checker of which links are colliding, in order to guide the selection of a relevant group of DOF to shortcut.

@@

We also experiment our algorithm on more complex robots and environments.
In the included video and Figures~\ref{pr2_final},~\ref{fiad} 
and~\ref{fig:trajectories}, we present multiple situations where the GB algorithm 
is tested and compared to RS~\cite{randomShortcutHPP}
(Algorithm~\ref{algo:random-shortcut}) and PRS~\cite{partialrandomShortcutHPP} 
adapted from~\cite{Geraerts04clearancebased}.
The termination condition of RS allows it to try 
shortening the path until five iterations of non-improvement are reached. 
This corresponds to $maxNbFailures$ in (Algorithm~\ref{algo:random-shortcut}).
For our implementation of PRS, first a shortcut is tried on each DOF between 
$\conf_0$ and $\conf_{wp+1}$. 
Then, for each DOF, configurations are sampled as in 
(Algorithm~\ref{algo:random-shortcut}). The steering-method returns a path made of 
an interpolation on only 
the current DOF and based on the previous subpath for other DOF. If this path is 
collision-free, we replace it as in RS. This process is also stopped when five 
iterations of non-improvement are reached.

\vspace{0.4cm}
% freeflyer puzzle
Before entering the manipulator examples, the GB algorithm is analyzed 
on a popular problem in the motion planning literature: a freeflyer puzzle, 
corresponding to Figure~\ref{fig:trajectories:puzzle}. The 
puzzle has to cross down the 
obstacle using the hole in the middle. The initial path planned with Visibility-PRM 
contains detours above and below the obstacle, as well as small superfluous
motions in the hole. 
Lengths of initial, GB optimized, and RS optimized paths are 
respectively 23.4, 8.53 and 10.2. PRS fails to decrease the path length because in 
this problem, all DOF are closely related to cross the hole. This behavior was also 
noticed and improved in the PRS implementation of~\cite{Geraerts04clearancebased}, 
acting on a group of DOF. The GB optimizer manages to modify the puzzle trajectory 
even in the hole, contrary to RS which simply copies the initial path when the 
trajectory gets near of the obstacle. $\alpha_{init}$ is reduced to 0.05 to slightly modify the very constrained trajectory at each iteration.

>>>>

For this shortening purpose, random shortcut (RS) methods are
still very 
popular~\cite{Sekhavat-Svestka1998,GeraertsIJRR07,HauserFastSmooth}. 
However, RS requires fine 
tuning of the termination condition and is no efficient for long 
trajectories where only a minor part needs to be optimized, 
as in Figure~\ref{local_box_optim}.
Figure~\ref{decoupled_DOF_optimization} presents another situation where RS 
will always fail to optimize the initial path, since it cannot decouple the 
robot degrees of freedom (DOF) on which the optimization occurs. This problem is 
addressed by our method.

@@

Some heuristics use random shortcuts on the initial guess combined with a 
trajectory re-building. For example,~\cite{HauserFastSmooth} returns smooth shortcuts made of parabola and line combinations, relying on the classical bang-bang control approach. These local refined trajectories 
are time-optimal since they comply with acceleration and velocity constraints. 
Also based on random shooting,~\cite{Guernane2011} is guiding 
configuration-generation with local holonomic considerations. 
Nevertheless this method remains only 
locally optimal, and is not addressing high-DOF 
problems.~\cite{GeraertsIJRR07} is 
using medial axis retraction for clearance and a PRS (shortcut is applied only 
on some random DOF) 
which can address the problem of Figure~\ref{decoupled_DOF_optimization}. 
However it is 
relatively slower than RS, and~\cite{GeraertsIJRR07} only investigates 
it for freeflyer robots. 
Furthermore PRS is not taking advantage of information returned by 
the checker of which links are colliding, in order to guide the selection of a relevant group of DOF to shortcut.

@@

We also experiment our algorithm on more complex robots and environments.
In the included video and Figures~\ref{pr2_final},~\ref{fiad} 
and~\ref{fig:trajectories}, we present multiple situations where the GB algorithm 
is tested and compared to RS~\cite{randomShortcutHPP}
(Algorithm~\ref{algo:random-shortcut}) and PRS~\cite{partialrandomShortcutHPP} 
adapted from~\cite{GeraertsIJRR07}.
The termination condition of RS allows it to try 
shortening the path until five iterations of non-improvement are reached. 
This corresponds to $maxNbFailures$ in (Algorithm~\ref{algo:random-shortcut}).
For our implementation of PRS, first a shortcut is tried on each DOF between 
$\conf_0$ and $\conf_{wp+1}$. 
Then, for each DOF, configurations are sampled as in 
(Algorithm~\ref{algo:random-shortcut}). The steering-method returns a path made of 
an interpolation on only 
the current DOF and based on the previous subpath for other DOF. If this path is 
collision-free, we replace it as in RS. This process is also stopped when five 
iterations of non-improvement are reached.

\vspace{0.4cm}
% freeflyer puzzle
Before entering the manipulator examples, the GB algorithm is analyzed 
on a popular problem in the motion planning literature: a freeflyer puzzle, 
corresponding to Figure~\ref{fig:trajectories:puzzle}. The 
puzzle has to cross down the 
obstacle using the hole in the middle. The initial path planned with Visibility-PRM 
contains detours above and below the obstacle, as well as small superfluous
motions in the hole. 
Lengths of initial, GB optimized, and RS optimized paths are 
respectively 23.4, 8.53 and 10.2. PRS fails to decrease the path length because in 
this problem, all DOF are closely related to cross the hole. This behavior was also 
noticed and improved in the PRS implementation of~\cite{GeraertsIJRR07}, 
acting on a group of DOF. The GB optimizer manages to modify the puzzle trajectory 
even in the hole, contrary to RS which simply copies the initial path when the 
trajectory gets near of the obstacle. $\alpha_{init}$ is reduced to 0.05 to slightly modify the very constrained trajectory at each iteration.
